---
title: "test for two proportions"
output: html_document
date: "2022-12-22"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Tests for the difference of 2 proportions 

## A groceries store want to upgrade its website, 
## so it can promote the salse online. They arranged to 
## conduct a survey before and after the upgrade.

## Before the change there are 671 out of 1000 people, 
## who are positive about the website, while it has 649 
## out of 950 peope, who are in favor of the 'new' design. 

## Do you think the new desing made a difference or not ?

## We can construct a confidence interval to see this

```{r}
p1 = 671 / 1000
n1 = 1000

p2 = 649 / 950
n2 = 950
```

```{r}
## we will use 95% confidence level, which has a 
## Z-score 1.96 as approximation 
Z_score = 1.96
```

```{r}
# CI is calculated use a list in R
(p2 - p1) + c(-Z_score * sqrt(p2*(1-p2)/n2 + p1*(1-p1)/n1),
            Z_score * sqrt(p2*(1-p2)/n2 + p1*(1-p1)/n1))
```

## CI -0.02935546  0.05367125
## it is include 0, in this interval, so, 
## the difference between the new and
## old website is not significant. No difference made. 

